### 2017-06-18 src/algorithm.tex
alg

We now show how to compute the optimal embedding.
Let $C(w_v, w_p)$ denote the
optimal embedding of a $s_vw_v$-path into a $s_pw_p$-path.
Let $\pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(w_v, w_p) = 
\min_{\substack{
u_v : pi(u_v) \leq pi(v_v), 
\\
v_pw_p \in A_p
}}
C(u_v, u_p)
+
\argmin_{C : P_{w_p}(v_v, w_v, C) \leq p_c(w_p)}
\\
&C(s_v, w_p) = c(s_v, w_p)
\end{align*}
We note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v,
C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

>>>>

We now show how to compute the optimal embedding.
Let $C(w_v, w_p)$ denote the
optimal embedding of a $s_vw_v$-path into a $s_pw_p$-path.
Let $\pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(w_v, w_p) = 
\min_{\substack{
u_v : pi(u_v) \leq pi(v_v), 
\\
v_pw_p \in A_p
}}
C(u_v, u_p)
+
\argmin_{C : P_{w_p}(v_v, w_v, C) \leq p_c(w_p)}
\\
&C(s_v, w_p) = c(s_v, w_p)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(t_v, t_p)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v, C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.
